\documentclass{article}

\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{Ruicheng Wu}
\rhead{07/4/2017}
\chead{Homework 3}

\begin{document}
1.total is $C(52,7)= 133784560$

a.\\Choose the rank of four cards: 13 ways\\Choose the suits of those four cards: 1 way\\Choose the rank for rest three cards:12 ways\\Choose the suits for these three cards : $C(4,3) = 4$ ways, thus the probability is $$13*1*12*4/133784560 = 0.00000466421$$

b.\\Choose the rank of three cards: 13 ways\\Choose the suits of those three cards: 4 ways\\Choose the two different ranks for rest cards:$C(12,2) = 66$ ways\\Choose the suits for these each two cards : $C(4,2)*C(4,2) = 36$ ways, thus the probability is $$13*4*66*36/133784560 = 0.00092351464 $$

c.\\Choose the three different rank of 6 cards: $C(13,3) = 286$ ways\\Choose the suits of those 6 cards: $C(4,2)*C(4,2)*C(4,2) = 216$  ways\\Choose the fourth rank for rest one card :10 ways\\Choose the suits for last one card : 4 ways. Thus the probability is $$286*216*10*4/133784560 = 0.01847029283 $$

d.\\Think the 7 consecutive ranks as a whole entity, there are $13-7+1 = 7$ spots to place the entity. Choose spot : 7 ways\\Choose suits for this entity: every rank has 4 ways, so it is $4^7$.  Thus the probability is $$4^7*7/133784560 = 0.00085725886 $$

2.\\Total is $6^6$ cases

a.\\There are 6! ways to have subset ${(1,2,3,4,5,6)}$,there are total $6^6$ ways. Thus,the probability is $6!/6^6 = 0.01543209876$

b.\\The total is $6^6= 46656$,treat sum $15$ as balls,6 dices are dividers. There are totally $15-1 = 14$ spaces to put $6-1=5$ dividers. There are $C(14,5)= 2002$ cases.However, we have to subtract total cases that is invalid 

$(1,1,1,1,1,10),(1,1,1,1,2,9),(1,1,1,1,3,8)$

$(1,1,1,1,4,7),(1,1,1,2,2,8),(1,1,1,2,3,7),(1,1,2,2,2,7)$

All permutations are :$C(6,1)+C(6,2)*3*2+3*C(6,2)*C(4,1)+C(6,3)*3*2+C(6,3)*C(3,1) = 456$. So there are totally : $2002-456=1546$ ways to have sum of 15. Thus the probability is $1546/46656 = 0.0331361454 $

c.\\This time, first distribute $3$ to green dice. Then there is only $12$ as sum. By performing same method. $C(11,5)=462$ Cases that has at 4 at green dice. There are still invalid cases existing $(4,1,1,1,1,7)$. There are $6$ cases. By subtraction rule, $(462-6)/46656 = 0.00977366255$.

d.\\Find situation with at least 1, choose dice to be 1 and rest to be any ： $6^5/6^6$.By subtraction, $1-(6^5/6^6)$ is the event that number on each of dice is at least 2.

e.\\Each number is $1/6$.
Choice 1: 2 dice to be 2$C(6,2)$.
Choice 2:2 dice to be 4$C(4,2)$.
Choice 3:2 dice to be 6$C(2,2)$.
Grand total :$(1/6)^6*C(6,2)*C(4,2)*C(2,2)= 0.00192901234$

3.\\Both sides contains $r$,$n$. $r \leq n$.

Both sides are counting the ways to choose team with $r$ leaders from $n$ people.

LHS:Think as choose a team with size of $k$ from $n$ people, $k \leq n$.Then from those $k$ people, choose $r$ leaders.$r$ may equal $k$.
RHS:In this case, first choose $r$ leaders from $n$ people : $C(n,r)$. Since $r  \leq n$, the rest team member totally has $2^{n-r}$ ways to choose. By multiplication rule, the total is $C(n,r)*2^{n-r}$.
LHS choose $k$ team members as well as choosing $r$ leaders with all situation of $k \leq n$. RHS choose $r$ leaders from $n$ people,then counts all different situations for choosing rest team members.They are actually counting the same thing

\end{document}